A Switching Planner for Combined Task and Observation Planning

### 2011-02-05 subarchitectures/planner.sa/trunk/src/latex/AAAI11/conc.tex
experimental results section is still shit! I don't get the task f problem yet

%% From an automated planning perspective, the problem of practical
%% mobile robot control poses important and contrary challenges.
%% %%
%% On the one hand, planning and execution monitoring must be
%% lightweight, robust, timely, and should span the lifetime of the
%% robot. Those processes must seamlessly accommodate exogenous events,
%% changing objectives, and the underlying unpredictability of the
%% environment.
%% %%
%% On the other hand, robot planning should perform computationally
%% expensive reasoning about contingencies, and possible revisions of
%% subjective belief according to quantitatively modelled uncertainty in
%% acting and sensing.

For use in an integrated continual planning and execution monitoring
system on a mobile robot platform, we developed a base planner that
switches between fast sequential and expensive decision-theoretic
planning. Given a POMDP model of the environment, sequential planning
is used to compute an initial deterministic sequential plan and
complementary runtime evolution of the decision process. That plan is
executed until testing of an assumption about the runtime state is
scheduled. At that point a contingent session performs some sensing
which determines whether or not the sequential session should be
allowed to continue, or otherwise acts to achieve the overall
objectives.

The most pressing item for future research, is to develop a scheme
whereby the serial planner can relax {\em executability} assumptions,
so that conformant (or semi-conformant) plans can be executed without
interruption by a contingent session. A more general criticism of
switching continual planning concerns interleaved sequential and
contingent sessions failing to make any progress towards the
objectives. For example, in the worst case we can have each sequential
session producing an identical plan, and each decision-theoretic
session rejecting it without further sensing. Although this has not
been an issue in our work so far, it must be dealt with rigorously
in the future. We suggest that a good way to mitigate this problem is
by developing a {\em motivational} component that maintains a {\em
dynamic} reward model whose limiting behaviour prevents that switching
deadlock.

>>>>

For use in an integrated continual planning and execution monitoring
system on a mobile robot platform, we developed a base planner that
switches between fast sequential and expensive decision-theoretic
planning. Given a DTPDDL model of the environment, sequential planning
is used to compute an initial deterministic sequential plan and
complementary runtime evolution of the decision process. That plan is
executed until testing of an assumption about the runtime state is
scheduled. At that point a contingent session performs some sensing
which determines whether or not the sequential session should be
allowed to continue, or otherwise acts to achieve the overall
objectives. We find our approach performs quickly and relatively
efficiently in large real-world task and observation planning
problems.

\Omit{
The most pressing item for future research, is to develop a scheme
whereby the serial planner can relax {\em executability} assumptions,
so that conformant (or semi-conformant) plans can be executed without
interruption by a contingent session. A more general criticism of
switching continual planning concerns interleaved sequential and
contingent sessions failing to make any progress towards the
objectives. For example, in the worst case we can have each sequential
session producing an identical plan, and each decision-theoretic
session rejecting it without further sensing. Although this has not
been an issue in our work so far, it must be dealt with rigorously
in the future. We suggest that a good way to mitigate this problem is
by developing a {\em motivational} component that maintains a {\em
dynamic} reward model whose limiting behaviour prevents that switching
deadlock.
}
